% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage{mathpazo}
\renewcommand{\sfdefault}{ppl}

% moderncv themes
\moderncvtheme[orange]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[black]{classic}                % idem


% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.9]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Xinjiang}
\familyname{Shao}
%\title{University of Illinois at Chicago}               % optional, remove the line if not wanted
%\address{809 S. Damen Ave.}{Chicago, IL 60612}    % optional, remove the line if not wanted
%\extrainfo{809 S. Damen Ave.\\ Chicago,IL 60612}
\mobile{312-694-3955}                    % optional, remove the line if not wanted
%\phone{phone (optional)}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{shaoxinjiang(at)gmail.com}                      % optional, remove the line if not wanted
\homepage{shaoxinjiang.com}                % optional, remove the line if not wanted
%\extrainfo{} % optional, remove the line if not wanted
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Experience}
\cventry{2012-2015\newline(Four Years)}{Full Stack Developer}{EXACT Sport}{Chicago, IL}{USA}{
	\begin{itemize}
		\item Work directly with the VP of Technology and the CEO to define and lead product strategy. 
		\item Provide input in the design process and incorporate into overall application.
		\item Act as DevOps to build infrastructure for apps to be developed, deployed, scaled, backed up, optimized.
	\end{itemize}
}
\cventry{2011-2013\newline(Two Years)}{Web Developer}{Independent Freelancer}{Chicago, IL}{USA}{
	\begin{itemize}
		\item Make design recommendations for clients in need of blog-like websites and CMS based on Wordpress.  
		\item Optimize websites by various of techniques such as SEO, Images Resizing, CSS/JS minification etc. 
		\item Review, secure and remove malware invaded websites, especially for those based on Wordpress, Zen-Cart etc.
	\end{itemize}
}
\cventry{2011\newline(Six Months)}{C/C++ Developer}{Sagittarius Technology Co. Ltd. }{Shanghai}{P. R. China}{%
\begin{itemize}%
\item Responsible for developing acoustic fingerprinting system for Splayer in order to raise the accuracy of subtitle matching system.
\item Cooperate with Eaget which in Shenzhen, China to test new model(M9) of HD movie player with subtitle matching enabled.
\end{itemize}}

\section{Projects}
\cventry{2012-Present}{PrepHero}{Athletic Recruiting Service and Camp Registration Service}{}{}{
 	\begin{itemize}
 	\item Developed various of online psychological profiling applications for athletes and coaches which are also used by MLB, NHL and US Soccer prospects. 
 	\item Building RESTfull API Endpoints and iOS app for capturing and storing athletic highlight video clips.  
 	\item Migrated Our service to Amazon’s Web Service in order to get high scalability, availability, and faster
response time.
 	\end{itemize}
}
\cventry{2013-Present}{Fancy Foodie}{A Food Review App}{}{}{
 	\begin{itemize}
 	\item Designed whole user interface, logo and workflow solely. New logo designed by Zhechao.
 	\item Built with Objective-C and open sourced afterwards.
 	\item The app is the winner of the First Annual Competition hosted by UIC CS Department.
 	\end{itemize}
}
\cventry{2011}{Splayer - Subtitle Matching Branch}{A Media Player on Windows Platform}{}{}{
 	\begin{itemize}
 	\item Develop a server side application with load balancing enabled to get the distance of requsted hash and stored video hashes and responds back the most possible matched subtitle for the video
 	\item Merge with Splayer Client to be capable to calculating hash with perceptual hashing algorithms for a small clip of soundtrack in a video
 	\end{itemize}
}
\section{Education}
\cventry{2011--2013}{Master of Science in Computer Science}{University of Illinois at Chicago}{Chicago,USA}{\textit{}}{ }  % arguments 3 to 6 can be left empty
\cventry{2007--2011}{Bachelor of Science in Information and Computing Science}{Dalian Polytechnic University}{Dalian, P.R.China}{\textit{}}{}

\section{Skills}
\cvcomputer{Languages}{PHP, Objective-C, Javascript, HTML 5, Java}{}{}
\cvcomputer{Databases}{MongoDB, MySQL, Redis}{}{}
\cvcomputer{Others}{MVC, RESTful API, JSON, XML, AWS, Git}{}{}

\section{Languages}
\cvlanguage{Chinese}{Mother Tongue}{Fluent in writing, reading, speaking}
\cvlanguage{English}{Second Language}{Fluent in writing, reading; good in speaking}

%\section{Extra}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

\renewcommand{\listitemsymbol}{-} % change the symbol for lists



% Publications from a BibTeX file without multibib\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% for BibTeX numerical labels
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}       % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}   % 'publications' is the name of a BibTeX file

\end{document}

